COG-ED Manuscript

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
removed auc demo calculation

```{r AUC_demo, echo=FALSE, message=FALSE, warning=FALSE}

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:(nrow(demo_data)/4)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  #demo_data$sv[m:(m+3)] = sv[n,]
  demo_data$sv[m:(m+3)] = sample(x = c(0.11,0.38,0.45,0.53,0.70,0.85,0.90,1.00), size = 4, replace = FALSE, prob = c(0.025,0.025,0.05,0.05,0.05,0.05,0.05,0.7))
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(),
                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(), auc_x_ascentsum = double(),
                      auc_westbrook = double())
for (i in 1:(length(subjectindex)-1)) {
  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                   method = "trapezoid"),
                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3),
                        auc_x_ascentsum = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]])),
                        auc_westbrook = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[1] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[1] + sv_sorted[4]))/3)
  demo_sv <- rbind(demo_sv, newdata)
}
demo_cor <- cor(demo_sv$auc_sv, demo_sv$auc_westbrook)

ggplot(demo_data, aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1)

#library(data.table) for the melt function
ggplot(melt(setDT(demo_sv), id.vars = "subject", variable.name = "measure"), aes(fill=measure,y=value,x=subject)) + geom_bar(position = "dodge", stat = "identity")
```

@@

The AUC of SVs predicted a significant amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_axauc`).

@@

When including the AUC of all NASA-TLX subscales as a predictor, it could not explain any variance in NFC beyond the one explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).

>>>>

@@

The $AxAUC$ value did not predict any amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).

@@

When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
An increase in one NASA_NTLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).
